The Astropy Project:

### 2017-09-29 main.tex
component names

The classes that handle coordinate representations (the \texttt{Representation}
classes) act like three-dimensional vectors and thus support vector arithmetic.
The classes that represent reference systems and frames (the \texttt{Frame}
classes) internally use \texttt{Representation} objects to store the coordinate
data---that is, the \texttt{Frame} classes accept coordinate data, either as a
specified \texttt{Representation} object, or using short-hand keyword arguments
to specify the components of the coordinates.
Many of the \texttt{Frame} classes also have attributes specific to the
corresponding reference system that allow the user to specify the frame.
For example, the Fifth Fundamental Catalogue (FK5) reference system requires
specifying an equinox to determine the reference frame.

- With differential classes, frames support velocities

@@

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
	\item JPL ephemerids
    \item Proper motions, radial velocities
\end{itemize}

>>>>

The classes that handle coordinate representations (the \texttt{Representation}
classes) act like three-dimensional vectors and thus support vector arithmetic.
The classes that represent reference systems and frames (the \texttt{Frame}
classes) internally use \texttt{Representation} objects to store the coordinate
data---that is, the \texttt{Frame} classes accept coordinate data, either as a
specified \texttt{Representation} object, or using short-hand keyword arguments
to specify the components of the coordinates.
These preferred representation and short-hand component names differ between
various astronomical reference systems.
For example, in the ICRS frame, longitude and latitude are right ascension
(\texttt{ra}) and declination ((\texttt{dec})), whereas in the Galactic frame,
the spherical angles are Galactic longitude (\texttt{l}) and latitude
(\texttt{b}).
Each of the \texttt{Frame} classes define their own component names and
preferred \texttt{Representation} class.
The frame-specific component names map to corresponding components on the
underlying \texttt{Representation} object that interally stores the coordinate
data.
For most frames the preferred representation is spherical.

Many of the \texttt{Frame} classes also have attributes specific to the
corresponding reference system that allow the user to specify the frame.
For example, the Fifth Fundamental Catalogue (FK5) reference system requires
specifying an equinox to determine the reference frame.

todo: The typical user doesn't have to interact with the frame classes or
representation classes directly.
Instead, use the \texttt{SkyCoord} object...

@@

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
    \item differential classes
    \item Proper motions, radial velocities
    \item JPL ephemerids
\end{itemize}
